Balsa: A Compact Line Notation Based on SMILES

### 2022-06-25 manuscript.tex
Adds figure for implicit hydrogen count. closes #6

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Implicit hydrogen count. The number of hydrogens is set algorithmically.}
    \label{fig:implicit-hydrogen-count}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{implicit-hydrogen-count.pdf}
    \caption{Implicit hydrogen count. The number of hydrogens is computed algorithmically. For unselected atoms (top left, top right, bottom right), implicit hydrogen count equals subvalence. For selected atoms (bottom left), implicit hydrogen count equals subvalence minus one. The hydrogen count for an atom whose element lacks at least one default valence can not be determined algorithmically.}
    \label{fig:implicit-hydrogen-count}
\end{figure}
